### 2014-06-13 scratchwork/test.turboem.Rmd
corrected error in sign of objective function calculation for SQUAREM

Now try a bigger sample, just comparing EM and squareEM
```{r}
  set.seed(100)
  sampsize=500000
  sd = c(1,1.1,1.2)
  z = rnorm(sampsize,0,sample(sd,sampsize,replace=TRUE))
  lik = t(vapply(z,dnorm,sd,sd=sd))
  prior=c(1,1,1)
  pi.init=c(0.3,0.2,0.5)
  res = turboem(par=pi.init, control.run=list(convtype = "objfn",tol=1e-5),fixptfn=fixpoint, objfn=penloglik, pconstr=pconstr,method=c("em", "squarem"), matrix_lik=lik,prior=prior)
  options(digits=13)
  res
```

Now run the squarem package directly
```{r}
  library(SQUAREM)
  system.time(res3<-squarem(par=pi.init,fixptfn=fixpoint, objfn=penloglik,matrix_lik=lik, prior=prior))
```

>>>>

Now try a bigger sample, just comparing EM and squareEM
```{r}
  set.seed(100)
  sampsize=500000
  sd = c(1,1.1,1.2)
  z = rnorm(sampsize,0,sample(sd,sampsize,replace=TRUE))
  lik = t(vapply(z,dnorm,sd,sd=sd))
  prior=c(1,1,1)
  pi.init=c(0.3,0.2,0.5)
  res = turboem(par=pi.init, control.run=list(convtype = "objfn",tol=1e-5),fixptfn=fixpoint, objfn=negpenloglik, pconstr=pconstr,method=c("em", "squarem"), matrix_lik=lik,prior=prior)
  options(digits=13)
  res
```

Now run the squarem package directly
```{r}
  library(SQUAREM)
  system.time(res3<-squarem(par=pi.init,fixptfn=fixpoint, objfn=negpenloglik,matrix_lik=lik, prior=prior))
```
